---
title: "Preg_lifestyle"
author: "Kazi rahman"
date: "2022-11-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caTools)
library(car)
library(quantmod)
library(MASS)
library(corrplot)
library(mctest)
library(glmnet)
library(ggplot2)
library(GGally)
library(caret)
```

Assumptions:
Only categorical variables

## EDA

You can also embed plots, for example:

```{r data, echo=FALSE}
data<-read.csv('preg_data.csv')
#Checking for Nans
nan_count <-sapply(data, function(data) sum(length(which(is.na(data)))))
nan_count <- data.frame(nan_count)
nan_count
#Replacing Nans with mean
nan_rep<-mean(data$hs_correct_raven,na.rm = TRUE)
data[is.na(data)] =nan_rep

#Encoding character categorica values to numeric values
data$h_pamod_t3_None<-factor(data$h_pamod_t3_None,
                             level = c('None','Sometimes','Often','Very Often'),
                             label = c(0,1,2,3))
data$h_pavig_t3_None<-factor(data$h_pavig_t3_None,
                             level = c('Low','Medium','High'),
                             label = c(0,1,2))



```
Our covariate of interest or y, has 10 Nan values. The rest of our covariates
do not have any Nans which is a good sign. We have established a cleaner
dataset now. We can proceed onto visualizing our data to get a better 
understanding

```{r plots_data}
data_matrix<-data.matrix(data)
corr<-cor(data_matrix)
corr
ggpairs(data)
GenderPlot1 = ggplot(data, aes(x = data$e3_alcpreg_yn_None, y = data$hs_correct_raven)) + geom_boxplot() 
GenderPlot1
GenderPlot2 = ggplot(data, aes(x = data$h_cereal_preg_Ter, y = data$hs_correct_raven)) + geom_boxplot() 
GenderPlot2
corrplot(corr)
vif_values <- vif(M1) 
vif_values
mc.plot(M1)
```
Before proceding to our next step, which will be building the model,
we want to perform feature selection and possible test for interactions.

```{r feature_selection}
x<-data.matrix(data[,c("e3_alcpreg_yn_None" , "h_cereal_preg_Ter" ,
                            "h_dairy_preg_Ter" ,   "h_fastfood_preg_Ter",
                             "h_fish_preg_Ter" ,    "h_folic_t1_None"   ,  
                            "h_fruit_preg_Ter"   , "h_legume_preg_Ter"  , 
                            "h_meat_preg_Ter" ,   
                            "h_pamod_t3_None" ,    "h_pavig_t3_None"  ,   
                            "h_veg_preg_Ter")])

cv_model <- cv.glmnet(x, data$hs_correct_raven, alpha = 1)
best_lambda <- cv_model$lambda.min
best_lambda
#The lambda value that minimizes the test MSE turns out to be 0.04498289
plot(cv_model) 

best_model <- glmnet(x, data$hs_correct_raven, alpha = 1, lambda = best_lambda)
coef(best_model)

test_cov_ind<-which(coef(best_model)==0)
excluding_var<-c()
for (i in test_cov_ind){
  print(names(data[i]))
  excluding_var <- c(excluding_var, names(data[i]))
}
print("cov that we may exclude")
print(excluding_var)
DF <- read.csv('preg_data.csv')

df2<-subset(data,select = excluding_var)
df3<-DF[,!names(DF) %in% 
      excluding_var]


lass_model<-lm(data$hs_correct_raven~.,data = df3)
M2<-lm(data$hs_correct_raven~.,data = data)
anova(lass_model,M2)


#cereal and dair
#fish and folic
#fruits and physical activity
#step-wise
#laso and step-wise same dataet

```

